LEGWORK: A python package for computing the evolution and detectability \\ of stellar-origin gravitational-wave sources with space-based detectors

### 2021-11-16 src/ms.tex
add showyourwork reference

\software{\lw{} is written in \texttt{Python}, available from \url{https://www.python.org}. We make use of the following Python packages: \texttt{matplotlib} \citep{Hunter+2007}, \texttt{NumPy} \citep{2020NumPy-Array},
\texttt{Astropy} \citep[\url{http://www.astropy.org}][]{AstropyCollaboration+2013,AstropyCollaboration+2018}, \texttt{Seaborn} \citep{Waskom+2021}, \texttt{SciPy} \citep{2020SciPy-NMeth}, \texttt{Numba} \citep{numba} and \texttt{Schwimmbad} \citep{Price-Whelan+2017}.}

>>>>

\software{\lw{} is written in \texttt{Python}, available from \url{https://www.python.org}. We make use of the following Python packages: \texttt{matplotlib} \citep{Hunter+2007}, \texttt{NumPy} \citep{2020NumPy-Array},
\texttt{Astropy} \citep[\url{http://www.astropy.org}][]{AstropyCollaboration+2013,AstropyCollaboration+2018}, \texttt{Seaborn} \citep{Waskom+2021}, \texttt{SciPy} \citep{2020SciPy-NMeth}, \texttt{Numba} \citep{numba} and \texttt{Schwimmbad} \citep{Price-Whelan+2017}. This paper was compiled using \texttt{showyourwork} \citep{Luger+2021}.}
